\bf Visual Inference for a Social Network Model

### 2019-01-28 ASApaper/paper.Rnw
finish abstract

\bigskip
\begin{abstract}
Three of the most important assessments of a statistical model are significance tests of parameters, goodness-of-fit tests, and power calculations of the tests. All three tasks become more difficult as the model becomes more complex. We will explore the three assessments of one particularly complex set of models, continuous time Markov chain (CTMC) models, for dynamic social networks  \citep{saompaper}. In this paper, we propose new methods for significance and goodness-of-fit testing, as well as power calculation for CTMC models via the visual inference (VI) paradigm of \citet{Bujaetal}. With VI, we can look at entire datasets simulated from a model, instead of relying a single metric such as a $p$-value for a single parameter in the model or goodness-of-fit assessed by looking at outdegree. We conducted an experiment through Amazon Mechanical Turk to assess the significance of parameters, the fit of a model, and the visual power of parameters.  
\end{abstract}

>>>>

\bigskip
\begin{abstract}
Three of the most important assessments of a statistical model are significance tests of parameters, goodness-of-fit tests, and power calculations of the tests. All three tasks become more difficult as the model becomes more complex. We will explore the three assessments of one particularly complex set of models, continuous time Markov chain (CTMC) models, for dynamic social networks  \citep{saompaper}. In this paper, we propose new methods for significance and goodness-of-fit testing, as well as power calculation for CTMC models via the visual inference (VI) paradigm of \citet{Bujaetal}. With VI, we can look at entire datasets simulated from a model, instead of relying a single metric such as a $p$-value for a single parameter in the model or goodness-of-fit assessed by looking at outdegree. We conducted a VI experiment, with participants recruited via Amazon Mechanical Turk, to assess the significance of CTMC parameters, the fit of a CTMC model, and the visual power of CTMC parameters.  
\end{abstract}
